---
pagetitle: "HerbSpectra-Amazon · Amazon Spectral Herbarium Network"
description: "We train people across the Amazon to turn botanical collections into spectral herbaria."
---

```{r}
#| include: false
source("../R/herbspectra.R", encoding = "UTF-8", local = knitr::knit_global())
```

::: {.column-screen .hero}
```{r}
#| output: asis
hero_fotos_html()
```

::: hero-inner
::: hero-texto
[Amazon Spectral Herbarium Network]{.eyebrow}

<h1>A spectral herbarium is <span class="giro" data-palavras="training|collaboration|innovation|the Amazon">training</span></h1>

We train people across the Amazon to read the light reflected by leaves in botanical collections, building herbaria where every specimen keeps not only its shape but also its spectral signature.

::: hero-acoes
[Explore the courses <i class="bi bi-arrow-right"></i>](cursos.qmd){.btn-hs} [About the network](sobre.qmd){.btn-hs-ghost}
:::
:::
:::
:::

::: column-screen
```{r}
#| output: asis
agora_html("en")
```
:::

::: {.secao .column-page}
[How it works]{.eyebrow}

## From specimen to spectrum, in seconds

Amazonian herbaria hold decades of specimens identified by specialists. These collections can gain a new layer of information without cutting a single leaf.

```{r}
#| output: asis
fluxo_html("en")
```

::: {.origem .leitura}
<i class="bi bi-journal-text origem-ic"></i>

::: {}
**Want to dig deeper?** To learn more about spectral digitization of herbaria, read the paper [*Next-generation specimen digitization: capturing reflectance spectra from the world's herbaria*](https://doi.org/10.1111/nph.70645){target="_blank"} (Cavender-Bares et al., 2026), in *New Phytologist*, written by the international IHerbSpec group with Caroline C. Vasconcelos, Flávia M. Durgante and Michael J. G. Hopkins from our team.
:::
:::
:::

::: {.column-screen .faixa-escura}
::: faixa-inner
::: faixa-topo
:::: {}
[Where we have been]{.eyebrow}

## A network that grows with every course

Starting from the INPA Herbarium in Manaus, we bring the spectrometer, the protocol and hands-on practice to each partner herbarium, in Brazil and in neighbouring Amazonian countries.
::::

:::: {}
```{r}
#| output: asis
numeros_html("en")
```
::::
:::

```{r}
#| output: asis
mapa_html("en", altura = "560px")
```

<p style="margin-top:1.4rem"><a class="link-seta" href="cursos.html">See all courses</a></p>
:::
:::

::: {.secao .column-page}
[In numbers]{.eyebrow}

## What the network has built so far

Training, science and tools: a snapshot of what HerbSpectra-Amazon has achieved to date.

```{r}
#| output: asis
indicadores_html("en")
```
:::

::: {.secao .column-page}
[What we do]{.eyebrow}

## Training people is at the heart of the project

Technology only transforms a collection when there are people ready to use it. That is why every stage of HerbSpectra-Amazon begins and ends with training.

::: cards
::: card-hs
<i class="bi bi-people card-ic"></i>

### Workshops in the herbaria

Three to five days of hands-on practice with the spectrometer and the international protocol, inside each network herbarium.
:::

::: card-hs
<i class="bi bi-laptop card-ic"></i>

### Online courses

The fundamentals of spectroscopy applied to botanical collections, in Portuguese and Spanish, open to the whole region.
:::

::: card-hs
<i class="bi bi-diagram-3 card-ic"></i>

### A shared protocol

Every herbarium measures its specimens the same way, so the data can be combined into a single collection.
:::

::: card-hs
<i class="bi bi-database card-ic"></i>

### A spectral database

Spectra linked to the name, locality and herbarium of each specimen form a standardized database for research, teaching and conservation.
:::
:::
:::

::: {.secao .column-page}
[In our courses]{.eyebrow}

## People learning together

From classrooms to herbarium cabinets: a few moments from our workshops.

```{r}
#| output: asis
galeria_html("en", n = 4)
```

<p><a class="link-seta" href="cursos.html#galeria">More photos and courses</a></p>
:::

::: {.secao .column-page}
::: destaque
We want every herbarium in the Amazon to be able to read, keep and share the spectral information of its own collection.
:::

::: origem
<i class="bi bi-arrow-repeat origem-ic"></i>

::: {}
**Where we come from.** HerbSpectra-Amazon extends to the whole Amazon the experience of [SpectraPop](https://spectrapop.github.io/){target="_blank"}, a project that developed and popularized a spectral herbarium of timber species in Amazonas, Brazil.
:::
:::


```{r}
#| output: asis
logos_html("en")
```
:::
